sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-11-19 doc/paper.Rmd
finer coastlines

```{r}
g_pred <- ggplot(bc_coast_proj) + geom_sf(
                                           # colour=NA, fill="white"
                                           fill=NA, colour="gray30"
                                           # fill="gray70", colour=NA
                                          ) +
  geom_raster(data = p, aes(x = X * 1000, y = Y * 1000, fill = exp(est))) +
  coord_sf(datum = st_crs(utm_zone9)) +
  scale_x_continuous(limits = c(230957.7 + 105000, 1157991 - 570000),
    labels = function(x) paste0(x/1000)
  ) +
  scale_y_continuous(limits = c(5366427 + 270000, 6353456 - 513000),
    labels = function(x) paste0(x/1000)
  ) +  
  scale_fill_viridis_c(trans = "sqrt", option = "C") +
  # scale_fill_viridis_c(trans = "sqrt", option = "B", begin = 0.3) +
  labs(fill = "Predicted\ndensity (units)", x = "UTMs E (km)", y = "UTMs N (km)") +
  theme(
    # panel.background = element_rect(fill = "slategray1", colour= "white"), 
    legend.position = c(0.2, 0.2), legend.key.height = unit(10, "pt"))
```

@@

```{r pcod-fig, fig.cap="(ref:pcod-fig-cap)", fig.width=9, out.width="5.2in", fig.asp=1, fig.align='center'}
g_omega <- ggplot(bc_coast_proj) + geom_sf(
                                           # colour=NA, fill="white"
                                           fill=NA, colour="gray30"
                                           # fill="gray70", colour=NA
                                           ) +
  geom_raster(data = p, aes(x = X * 1000, y = Y * 1000, fill = omega_s)) +
  coord_sf(datum = st_crs(utm_zone9)) +
  scale_x_continuous(limits = c(230957.7 + 105000, 1157991 - 570000),
    labels = function(x) paste0(x/1000)
  ) +
  scale_y_continuous(limits = c(5366427 + 270000, 6353456 - 513000),
    labels = function(x) paste0(x/1000)) +
  # scale_fill_gradient2(high = reds[4], low = scales::muted("purple")) +
  scale_fill_gradient2(high = reds[4], low = blues[4]) +
  labs(fill = "Spatial random\nfield deviations", x = "UTMs E (km)", y = "UTMs N (km)") +
  theme(
    # panel.background = element_rect(fill = "slategray1", colour= "white"),
    legend.position = c(0.2, 0.2), legend.key.height = unit(10, 'pt'))

>>>>

```{r}
g_pred <- ggplot(bc_coast_proj) + geom_sf(
                                           # colour=NA, fill="white"
                                           fill=NA, colour="gray30", lwd = 0.3
                                           # fill="gray70", colour=NA
                                          ) +
  geom_raster(data = p, aes(x = X * 1000, y = Y * 1000, fill = exp(est))) +
  coord_sf(datum = st_crs(utm_zone9)) +
  scale_x_continuous(limits = c(230957.7 + 105000, 1157991 - 570000),
    labels = function(x) paste0(x/1000)
  ) +
  scale_y_continuous(limits = c(5366427 + 270000, 6353456 - 513000),
    labels = function(x) paste0(x/1000)
  ) +  
  scale_fill_viridis_c(trans = "sqrt", option = "C") +
  # scale_fill_viridis_c(trans = "sqrt", option = "B", begin = 0.3) +
  labs(fill = "Predicted\ndensity (units)", x = "UTMs E (km)", y = "UTMs N (km)") +
  theme(
    # panel.background = element_rect(fill = "slategray1", colour= "white"), 
    legend.position = c(0.2, 0.2), legend.key.height = unit(10, "pt"))
```

@@

```{r pcod-fig, fig.cap="(ref:pcod-fig-cap)", fig.width=9, out.width="5.2in", fig.asp=1, fig.align='center'}
g_omega <- ggplot(bc_coast_proj) + geom_sf(
                                           # colour=NA, fill="white"
                                           fill=NA, colour="gray30", lwd = 0.3
                                           # fill="gray70", colour=NA
                                           ) +
  geom_raster(data = p, aes(x = X * 1000, y = Y * 1000, fill = omega_s)) +
  coord_sf(datum = st_crs(utm_zone9)) +
  scale_x_continuous(limits = c(230957.7 + 105000, 1157991 - 570000),
    labels = function(x) paste0(x/1000)
  ) +
  scale_y_continuous(limits = c(5366427 + 270000, 6353456 - 513000),
    labels = function(x) paste0(x/1000)) +
  # scale_fill_gradient2(high = reds[4], low = scales::muted("purple")) +
  scale_fill_gradient2(high = reds[4], low = blues[4]) +
  labs(fill = "Spatial random\nfield deviations", x = "UTMs E (km)", y = "UTMs N (km)") +
  theme(
    # panel.background = element_rect(fill = "slategray1", colour= "white"),
    legend.position = c(0.2, 0.2), legend.key.height = unit(10, 'pt'))
